Resource Adequacy and Operational Security Interaction in the EPOC 2030-50 Project

### 2022-05-27 papers/main.tex
Change initial state of charge
Alter reserve shedding sensitivity analysis

\begin{table}[H]
    \centering
    \begin{tabular}{ccccc}
        \toprule
        UC  & DANet & PSCD & Load shedding [MWh] & Objective \\
        \midrule
            &       &      & 0.0                 & 101,916   \\
        \xm &       &      & 0.0                 & 212,558   \\
        \xm & \xm   &      & 0.0                 & 252,327   \\
        \xm & \xm   & \xm  & 0.0                 & 252,327   \\
        \bottomrule
    \end{tabular}
    \caption{Analysis of model results when operating reserves are not included. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints.}\label{tab:results_no_OR}
\end{table}

@@

\begin{table}[ht]
    \centering
    \footnotesize
    \begin{tabular}{ccccccc}
        \toprule
        UC  & DANet & PSCD & RSL & Load shedding [MWh] & Reserve Shedding [MWh] & Objective \\
        \midrule
            &       &      & 0.0 & 0.0                 & 0.0                    & 117,290   \\
            &       &      & 0.5 & 0.0                 & 0.0                    & 117,290   \\
            &       &      & 1.0 & 0.0                 & 0.0                    & 117,290   \\
        \midrule
        \xm &       &      & 0.0 & 1,669               & 0.0                    & 645,679   \\
        \xm &       &      & 0.5 & 1,669               & 0.0                    & 645,679   \\
        \xm &       &      & 1.0 & 1,669               & 0.0                    & 645,679   \\
        \midrule
        \xm & \xm   &      & 0.0 & 1,669               & 0.0                    & 665,010   \\
        \xm & \xm   &      & 0.5 & 1,669               & 136                    & 657,010   \\
        \xm & \xm   &      & 1.0 & 1,669               & 136                    & 657,010   \\
        \midrule
        \xm & \xm   & \xm  & 0.0 & 1,669               & 0.0                    & 665,705   \\
        \xm & \xm   & \xm  & 0.5 & 1,669               & 136                    & 665,696   \\
        \xm & \xm   & \xm  & 1.0 & 1,669               & 136                    & 665,696   \\
        \bottomrule
    \end{tabular}
    \caption{Analysis of model results with operating reserves but no reserve activation network constraints. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints, RSL = Reserve Shedding Limit.}\label{tab:results_no_RANet}
\end{table}

@@

\begin{table}[ht]
    \centering
    \footnotesize
    \begin{tabular}{cccccccc}
        \toprule
        UC  & DANet & PSCD & AbsImb & RSL & Load shedding [MWh] & Reserve Shedding [MWh] & Objective \\
        \midrule
            &       &      &        & 0.0 & 34,860              & 0                      & 7,827,724 \\
            &       &      &        & 0.5 & 16,346              & 19,257                 & 3,934,989 \\
            &       &      &        & 1.0 & 7,521               & 28,209                 & 2,463,656 \\
        \midrule
        \xm &       &      &        & 0.0 & 34,860              & 0                      & 7,969,802 \\
        \xm &       &      &        & 0.5 & 16,672              & 19,002                 & 4,133,637 \\
        \xm &       &      &        & 1.0 & 9,190               & 26,809                 & 2,892,401 \\
        \midrule
        \xm & \xm   &      &        & 0.0 & 42,008              & 0                      & 9,572,369 \\
        \xm & \xm   &      &        & 0.5 & 16,950              & 28,096                 & 4,310,407 \\
        \xm & \xm   &      &        & 1.0 & 15,482              & 29,604                 & 4,029,268 \\
        \midrule
        \xm & \xm   & \xm  &        & 0.0 & 42,008              & 0                      & 9,572,828 \\
        \xm & \xm   & \xm  &        & 0.5 & 16,950              & 28,096                 & 4,310,407 \\
        \xm & \xm   & \xm  &        & 1.0 & 15,482              & 29,604                 & 4,029,268 \\
        \midrule
        \xm & \xm   & \xm  & \xm    & 0.0 & 42,008              & 0                      & 9,572,828 \\
        \xm & \xm   & \xm  & \xm    & 0.5 & 16,950              & 28,096                 & 4,310,407 \\
        \xm & \xm   & \xm  & \xm    & 1.0 & 15,482              & 29,604                 & 4,029,268 \\
        \bottomrule
    \end{tabular}
    \caption{Analysis of model results with operating reserves and with reserve activation network constraints with load multiplied by a factor of 1.5. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints, RSL = Reserve Shedding Limit.}\label{tab:results_no_RANet}
\end{table}

@@

Closer investigation at load shedding patterns for the model with UC and DANet (but no PSCD and AbsImb) reveals that all load shedding occurs at the start of the day (when the battery has not charged yet).

\todo[inline]{Load is shed at nodes where no load exists, which is clearly unphysical.}

>>>>

\begin{table}[H]
    \centering
    \begin{tabular}{ccccc}
        \toprule
        UC  & DANet & PSCD & Load shedding [MWh] & Objective \\
        \midrule
            &       &      & 0.0                 & 101,915   \\
        \xm &       &      & 0.0                 & 109,148   \\
        \xm & \xm   &      & 0.0                 & 227,495   \\
        \xm & \xm   & \xm  & 0.0                 & 227,492   \\
        \bottomrule
    \end{tabular}
    \caption{Analysis of model results when operating reserves are not included. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints.}\label{tab:results_no_OR}
\end{table}

@@

\begin{table}[ht]
    \centering
    \footnotesize
    \begin{tabular}{ccccccc}
        \toprule
        UC  & DANet & PSCD & RSL & Load shedding [MWh] & Reserve Shedding [MWh] & Objective \\
        \midrule
            &       &      & 0.0 & 0.0                 & 0.0                    & 101,345   \\
            &       &      & 0.5 & 0.0                 & 0.0                    & 101,014   \\
            &       &      & 1.0 & 0.0                 & 0.0                    & 101,014   \\
        \midrule
        \xm &       &      & 0.0 & 1.669               & 0.0                    & 617,536   \\
        \xm &       &      & 0.5 & 1.669               & 0.0                    & 617,536   \\
        \xm &       &      & 1.0 & 1.669               & 0.0                    & 617,536   \\
        \midrule
        \xm & \xm   &      & 0.0 & 1.669               & 0.0                    & 650,647   \\
        \xm & \xm   &      & 0.5 & 1.669               & 136                    & 650,231   \\
        \xm & \xm   &      & 1.0 & 1.669               & 136                    & 650,231   \\
        \midrule
        \xm & \xm   & \xm  & 0.0 & 1.669               & 0.0                    & 650,647   \\
        \xm & \xm   & \xm  & 0.5 & 1.669               & 136                    & 650,231   \\
        \xm & \xm   & \xm  & 1.0 & 1.669               & 136                    & 650,263   \\
        \bottomrule
    \end{tabular}
    \caption{Analysis of model results with operating reserves but no reserve activation network constraints. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints, RSL = Reserve Shedding Limit.}\label{tab:results_no_RANet}
\end{table}

@@

\begin{table}[ht]
    \centering
    \footnotesize
    \begin{tabular}{cccccccc}
        \toprule
        UC  & DANet & PSCD & AbsImb & RSL & Load shedding [MWh] & Reserve Shedding [MWh] & Objective \\
        \midrule
            &       &      &        & 0.0 & 32,366              & 0                      & 7,290,909 \\
            &       &      &        & 0.5 & 0.0                 & 36,269                 & 447,102   \\
            &       &      &        & 1.0 & 0.0                 & 36,082                 & 440,467   \\
        \midrule
        \xm &       &      &        & 0.0 & 32,366              & 0                      & 7,433,785 \\
        \xm &       &      &        & 0.5 & 1,669               & 34,379                 & 924,686   \\
        \xm &       &      &        & 1.0 & 1,669               & 34,308                 & 919,363   \\
        \midrule
        \xm & \xm   &      &        & 0.0 & 33,929              & 0                      & 7,822,959 \\
        \xm & \xm   &      &        & 0.5 & 1,967               & 39,234                 & 1,249,422 \\
        \xm & \xm   &      &        & 1.0 & 1,941               & 39,160                 & 1,245,647 \\
        \midrule
        \xm & \xm   & \xm  &        & 0.0 & 33,929              & 0                      & 7,822,959 \\
        \xm & \xm   & \xm  &        & 0.5 & 1,967               & 39,234                 & 1,249,422 \\
        \xm & \xm   & \xm  &        & 1.0 & 1,941               & 39,160                 & 1,245,647 \\
        \midrule
        \xm & \xm   & \xm  & \xm    & 0.0 & 33,929              & 0                      & 7,822,959 \\
        \xm & \xm   & \xm  & \xm    & 0.5 & 1,967               & 39,234                 & 1,249,422 \\
        \xm & \xm   & \xm  & \xm    & 1.0 & 1,941               & 39,160                 & 1,245,647 \\
        \bottomrule
    \end{tabular}
    \caption{Analysis of model results with operating reserves and with reserve activation network constraints with load multiplied by a factor of 1.5. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints, RSL = Reserve Shedding Limit.}\label{tab:results_no_RANet}
\end{table}

\todo[inline]{Objective is weird for some cases...}

@@

% Closer investigation at load shedding patterns for the model with UC and DANet (but no PSCD and AbsImb) reveals that all load shedding occurs at the start of the day (when the battery has not charged yet).

\begin{figure}[H]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../plots/main_model_runs/ls_per_node_idx=63}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../plots/main_model_runs/ls_per_node_idx=63}
        \caption{}
    \end{subfigure}
    \caption{}
\end{figure}
